---
title: "R Notebook"
author: "Ronak Songara"
date: "16/07/2021"
output:
  html_notebook: default
  html_document:
    df_print: paged
  pdf_document: default
---

# RAMEN NOODLES Analysis

## ask & prepare


#### load tidyverse package

```{r}
library(tidyverse)
```


#### read 'ramen ratings' dataset

```{r}
ramen_df <- read_csv("ramen-ratings.csv")
```
#### have a quick look on dataset with head,str functions

```{r}
head(ramen_df)
```

```{r}
str(ramen_df)
```


```{r}
summary(ramen_df)
```
#### how many unique brands are out there in global market ?
```{r}
n_distinct(ramen_df$Brand)
```

#### how many style of unique packaging ?
```{r}
n_distinct(ramen_df$Style)
unique(ramen_df$Style)
```


```{r}
library(skimr)
skim(ramen_df)
```

#### convert data type from character to float in 'stars' column and separate top ramen noodles

```{r}
ramen_df <- ramen_df %>%
  mutate(TopTenRanknigYear = str_sub(`Top Ten`,1,4),TopTenRanking = str_sub(`Top Ten`,7))
```

```{r}
within(ramen_df,rm(TopTenRaning))
```
```{r warning=FALSE}
ramen_df <- ramen_df %>%
  mutate(Stars = as.double(Stars))
```

## process

#### Q1: Country wise packaging styles?

```{r}
ggplot(ramen_df)+
  geom_bar(mapping = aes(x = Style, fill = Style,))+
  facet_wrap(~Country)+
  labs(title = "country wise packaging style chart")
```

#### Q2: Country wise ramen rating bar chart?

```{r}
ggplot(ramen_df)+
  geom_bar(mapping = aes(x = Stars, fill = Style,))+
  facet_wrap(~Country)+
  labs(title = "country wise rating chart according to packaging style")

```

```{r}
ramen_df2 = ramen_df
```

#### gropuby country and findout mean ramen rating and plot a bar chart.



```{r}
ramen_df3 <- ramen_df2 %>%
  group_by(Country) %>%
  summarise(mean_rating = mean(Stars)) %>%
  arrange(desc(mean_rating)) %>%
  print
```

```{r}
ggplot(ramen_df3)+
  geom_col(mapping = aes(y = Country,x = mean_rating))+
  theme(axis.text.x = element_text(angle = 45))+
  labs(title = "country wise mean rating")
```

#### also different kind of ramen packaging.

```{r}
ggplot(ramen_df)+
  geom_bar(mapping = aes(x = Country, fill = Style))+
  theme(axis.text.x = element_text(angle = 45))+
  labs(title = "country wise ramen packaging")
```

#### Q3. Which top 10 company share highest order in global market?


```{r}
ramen_df7 <- ramen_df2 %>%
  group_by(Brand) %>%
  summarise(quantity = n()) %>%
  arrange(desc(quantity)) %>%
  top_n(10) %>%
  print
```


```{r}
ggplot(ramen_df7) +
  geom_col(mapping = aes(x = quantity,y = Brand))+
  labs(title = "leading Ramen brands")
```
#### Q4: which kind of packing style are out there sharing percentage in global market?

```{r}
ramen_df5 <- ramen_df2 %>%
  count(Style, name = "number_of_styles",sort = TRUE) %>%
  mutate(percent_share_by_style = number_of_styles/sum(number_of_styles)*100) %>%
  print
```

```{r}
ggplot(ramen_df5)+
  geom_col(mapping = aes(x=Style,y=number_of_styles))+
  labs(title = "Ramen packing styles")
```

#### Q5: Which country order the most and there mean ratings ?

```{r}
ramen_df6 <- ramen_df %>%
  group_by(Country) %>%
  summarise(quantity = n(),mean_per_country = mean(Stars)) %>%
  arrange(-quantity) %>%
  print
```

```{r}
ggplot(ramen_df6) +
  geom_col(mapping = aes(x = quantity, y = Country))+
  labs(title = "countries order the most Ramen noodles")
```


